Comparing Power Optimizations in the Reorder Buffer

### 2011-06-12 paper/end.tex
more future works

>>>>

\section{Future Works}
We have proposed a novel loosley cycle accurate power simulator for a processor's
ROB.  With loose timing, the simulator is able to quickly simulate a stream of
instructions.  Furthermore by producing only the power tabulation, the simulator
remains flexible for future emerging technolgies in the underlying circut level.
This novel approach also allows for fair power effiency comparison between
existing and new designs.

Currently we have implemented four proposed designs.  This could be expanded covering 
more ROB designs. Since many of the techniques proposed for energy savings
are not mutally exclusion, a model could start combineing differnt modes.
Before preceeding forwards with more models, addtional tools may  be provided to
catch errornous results early on.  This could prove to be quite useful as currently
our output results do not make sense.  This could be a small bug in our source or
a misunderstanding of the mechinism for the ROB.

Additionally, we designed our simultor to be as modular as possible.  This allows
for future expansions on the simulator. This could include additional stages of 
the instruction lifetime such as the issue queue, or execution units.  With other
other component simulators a entire cycle accurate simulator could be created, with 
the flexibility to tune its accuracy and simulation run time. Another type of 
add-on module could be created and and translate our power tabulations into actual
power usages in joules.

Lastly further would could be expaned on our instruction generation.  As we 
currently generate synthetic instructions based on various profiles.  It would
be ideal to load in an actual instruction trace produced by alternative cycle 
accurate simulator.  This would
